### 2024-07-16 conteudo/background/linux.tex
Fix grammar by grammarly free tier

The Linux kernel is an Unix-like operating system published by Linus Torvalds in 1992 as a free software and
it started becoming popular in late 1990s \citep{linuxbook}. Against popular belief, linux is not a full 
operating system as it do not includes applications such as filesystem utilities, windowing systems. The "Linux" 
distributions know to the public are in fact GNU/Linux operating systems \citep{gnuref}.

TEXT ABOUT LINUX NUMBER SCOPE ETC.

The Linux project is organized as a set of subsystem such as process scheduler, memory management, 
device driver infrastruture, networking and filesystems \citep{melissa}.
Each subsystem usually have a maintainer or a group of maintainers, which are people responsible 
for managing and accepting contributions into the subsystem they care of it \citep{melissa}.

The contributions to the Linux are coordinate with the usage of the Git source management tool. The contributions 
made to the project are formated as patches, which are text documents describing differences between two different 
versions of a source tree \citep{melissa}.

TALK ABOUT HOW THE TOOL ENABLE A NEW WAY TO START CONTRITUTING TO THE KERNEL

AMD Display Driver is a linux's subsystem responsible for the management of AMD GPU's. This subsystem have a problem 
with code clone duplication acknowledged by the subsystem's maintainters. For this reason, we selected this
subsystem as the primary focus for our empirical analysis in our research.

>>>>

The Linux kernel is a Unix-like operating system published by Linus Torvalds in 1992 as a free software, and
it started becoming popular in the late 1990s \citep{linuxbook}. Against popular belief, Linux is not a full 
operating system as it does not include applications such as filesystem utilities or windowing systems. The "Linux" 
distributions known to the public are, in fact, GNU/Linux operating systems \citep{gnuref}.

The Linux kernel is monolithic and organized as a set of subsystems such as process scheduler, memory management, 
device driver infrastructure, networking, and filesystems \citep{melissa}.
Each subsystem usually has a maintainer or a group of maintainers.  Maintainers are people responsible 
for managing and accepting contributions to the subsystem they care for \citep{melissa}.

The contributions to Linux are coordinated with the usage of the Git source management tool.
The contributions to the project are formatted as patches, which are text documents describing differences 
between two different versions of a source tree The patches are sent and reviewed through the 
Linux mailing lists \citep{melissa}.

Mailing lists are the official means of communication of the Linux community, through the mailing lists 
the community members send and review contributions to the kernel, discuss topics related to Linux such as 
which new features to add, et cetera. As there are multiple subsystems in the Linux kernel, there are 
multiple mailing lists in the Linux to organize the discussion made. Every subsystem has its mailing 
list to concentrate the discussion related to the subsystem \citep{melissa}. 
The interactions made in the mailing lists are documented and stored in the Linux kernel Lore
\citep{linuxlore}, which serves as a repository of the discussion made in the Linux kernel to be
consulted by anyone interested.

One of the Linux kernel subsystems is the AMD Display Driver, a subsystem responsible for 
implementing the drivers required to enable AMD GPU to work properly in the Linux environment. 
The maintainers of this subsystem reported an empirical problem they have in the subsystem, which is 
a significant amount of duplicated code in the subsystem, which hinders the maintenance of the subsystem.
This reported problem is the starting point that initiated our research, making the AMD Display Driver our 
principal object of study to understand how to mitigate duplicated code in the Linux kernel.

(I WANT TO CHANGE THE AMD DISPLAY paragraph, WHY DO I NEED TO CHANGE IT? I SHOULD ANOTATE WHAT I WANTED, I MADE A CHANGE
 TO MAKE IT BETTER BUT NOT SURE IF THERE IS SOME INFORMATION I WANTED TO PUT IN IT, 
(MISSING AMD DISPLAY DRIVER MAILING LISTS, I WILL FIND IT LATTER)
